---
title: "R Markdown Presentation & Plotly"
author: "swsoyee"
date: "2017-9-30"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## 1. Introduction
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## 2. Review criteria
The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

**Example Submissions**

[Here](http://seankross.neocities.org/week3.html)'s an extremely minimal passing example, but we hope your submission is much cooler!

## 3. Installation
```{r}
# Check the Plotly package.
necessary <- c("plotly")
installed <- necessary %in% installed.packages()[, "Package"]

if (length(necessary[!installed]) >=1) {
  install.packages(necessary[!installed])
}
# Load and check the package.
library(plotly)
packageVersion("plotly")
```

## 4. Make a plot
```{r echo=FALSE}
p <- ggplot(data = iris, aes(x = Sepal.Length, 
                             y = Sepal.Width, 
                           col = Species))

p <- p + geom_point() + theme_bw()

ggplotly(p, tooltip = c("x", "y"))
```

